### 2020-04-12 draft_ABP.tex
Updates from Overleaf

For $0 \notin I $
\bea
x_I &=& \frac{\prod_{I \subset J} u_{J}}{1-\prod_{I \subset J} u_{J}} \\
\frac{1}{1+ x_I} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}}
\eea
From the above relations it is clear that taking $u_I \rightarrow 0$ for $0 \notin I$ implies $x_J \rightarrow 0$ for all $J \subset I$ and taking $u_\bar{I} \rightarrow 0$ for $0 \in I$ implies $x_J \rightarrow \infty $ for all $I \subset J$.
In fact we shall argue that there is unique choice of $x_I$'s which we can take to $0$ or $\infty$ which corresponds to setting a particular $u_I \rightarrow 0$ or $u_\bar{I} \rightarrow 0$ respectively.
\item From the definition of the permutahedron as a Nestohedron we know that $I$ and $J$ are :

@@

We shall prove $\mathscr P_{n+1}$ is binary by showing that whenever we take some $u_I \rightarrow 0$ (by taking a unique set of $x_i \rightarrow 0, \infty$) then $u_J \rightarrow 1$ for $J$ incompatible with $I$ and the remaining $u$'s reduce to the $u$'s corresponding to $\matchscr P_k \times \mathscr P_{n-k}$.

>>>>

For $0 \notin I $
\bea
x_I &=& \frac{\prod_{I \subset J} u_{J}}{1-\prod_{I \subset J} u_{J}} \\
\frac{1}{1+ x_I} &=& \prod_{{J}\atop{J\cap \bar{I} \ne \emptyset}} u_{\bar{J}}
\eea
From the above relations it is clear that taking $u_I \rightarrow 0$ for $0 \notin I$ implies $x_J \rightarrow 0$ for all $J \subset I$ and taking $u_{\bar{I}} \rightarrow 0$ for $0 \in I$ implies $x_J \rightarrow \infty $ for all $I \subset J$.
In fact we shall argue that there is unique choice of $x_I$'s which we can take to $0$ or $\infty$ which corresponds to setting a particular $u_I \rightarrow 0$ or $u_{\bar{I}} \rightarrow 0$ respectively.
\item From the definition of the permutahedron as a Nestohedron we know that $I$ and $J$ are :

@@

We shall prove $\mathscr P_{n+1}$ is binary by showing that whenever we take some $u_I \rightarrow 0$ (by taking a unique set of $x_i \rightarrow 0, \infty$) then $u_J \rightarrow 1$ for $J$ incompatible with $I$ and the remaining $u$'s reduce to the $u$'s corresponding to $\mathscr P_k \times \mathscr P_{n-k}$.
